Review of Assigned Readings

### 2017-12-27 documentation/documentation.tex
minor spelling mistakes and list of abbreviations

    \listoffigures 	
    \section*{List of Abbreviation} 
	\begin{acronym}[ASECRETTT] 
	\acro{API}{Application Programming Interface}
	\acro{CKEY}{Consumer Key}
	\acro{CSECRET}{Consumer Secret}
	\acro{ATOKEN}{Access Token}
	\acro{ASECRET}{Access Token Secret}
	\acro{JSON}{Java Script Object Notation}
	\end{acronym}
    \clearpage

@@

\subsubsection{Hardware Setup}
As explained in the previous section the twitter API was used to filter tweets in realtime based on the buzzword "bitcoin". The python program was running for seven days without interruption (to be checked!!!!!!!!!!!) on a raspberry pi (rpi) which was accessed with a secure shell (SSH) connection. This approach allowed us to ensure a continuous data stream while being able to access the program output regardless anywhere and anytime. Furthermore due to a low energy consumption of the rpi the method is also the most cost efficient one compared to a personal computer or NAS Server. The following section describes the different steps that have been taken in order to setup the rpi, ssh, git and python3.\newline The following steps were conducted by using a Raspberry Pi 2, a micro SD card and Python3 and Windows 10 64Bit.

@@

\item Download the collected data
\begin{enumerate}
\item Install FileZilla available from
\begin{lstlisting}[language=bash] 
https://filezilla-project.org/
\end{lstlisting}
\item Connect to rpi and navigate to data location \newline
\item Download data manually \newline \newline \end{enumerate}
\end{enumerate}
In summary, this approach worked quite well and run smoothly after all bugs have been resolved from the file CollectTwitterData.py A clean setup is crucial to ensure continuous data collection over a longer period.

>>>>

    \listoffigures 	
    \section*{List of Abbreviation} 
	\begin{acronym}[ASECRETTT] 
	\acro{API}{Application Programming Interface}
	\acro{ATOKEN}{Access Token}
	\acro{ASECRET}{Access Token Secret}
	\acro{CKEY}{Consumer Key}
	\acro{CSECRET}{Consumer Secret}
	\acro{JSON}{Java Script Object Notation}
	\acro{RPI}{Raspberry Pi}
	\acro{SSH}{Secure Shell}
	\end{acronym}
    \clearpage

@@

\subsubsection{Hardware Setup}
As explained in the previous section the twitter API was used to filter tweets in realtime based on the buzzword "bitcoin". The python program was running for seven days without interruption on a Raspberry Pi 2 (RPI) which was accessed with a Secure Shell (SSH) connection. This approach allowed us to ensure a continuous data stream while being able to access the program output regardless anywhere and anytime. Furthermore due to a low energy consumption of the RPI the method is also the most cost efficient one compared to a personal computer or NAS Server. The following section describes the different steps that have been taken in order to setup the RPI 2, SSH, Git and Python3.\newline

@@

\item Download the collected data
\begin{enumerate}
\item Install FileZilla available from
\begin{lstlisting}[language=bash] 
https://filezilla-project.org/
\end{lstlisting}
\item Connect to rpi and navigate to data location \newline
\item Download data manually \newline \newline \end{enumerate}
\end{enumerate}
In summary, this approach worked well and ran smoothly. A clean setup is recommended to ensure a continuous data stream over a longer period.
